BIP-Predictor

### 2025-05-20 Sweave/BIP_predictor.Rnw
up

inst_pack<-rownames(installed.packages())
if (!"mFilter"%in%inst_pack)
  install.packages("mFilter")
if (!"xts"%in%inst_pack)
  install.packages("xts")
if (!"MTS"%in%inst_pack)
  install.packages("MTS")
if (!"sandwich"%in%inst_pack)
  install.packages("sandwich")
if (!"multDM"%in%inst_pack)
  install.packages("multDM")
if (!"fGarch"%in%inst_pack)
  install.packages("fGarch")
if (!"xtable"%in%inst_pack)
  install.packages("xtable")
if (!"MASS"%in%inst_pack)
  install.packages("MASS")
if (!"glmnet"%in%inst_pack)
  install.packages("glmnet")

# Load the required R-libraries
# Standard filter package
library(mFilter)
# Multivariate time series: VARMA model for macro indicators: used here for simulation purposes only
library(MTS)
# HAC estimate of standard deviations in the presence of autocorrelation and heteroscedasticity
library(sandwich)
# Library for Diebold-Mariano test of equal forecast performance
library(multDM)
# GARCH model: for improving regression estimates
library(fGarch)
# Library for tables
library(xtable)
# Packages for Ridge and LASSO
library(MASS)
library(glmnet) 
# Extended time series
library(xts)

>>>>

inst_pack<-rownames(installed.packages())
if (!"mFilter"%in%inst_pack)
  install.packages("mFilter")
if (!"xts"%in%inst_pack)
  install.packages("xts")
if (!"MTS"%in%inst_pack)
  install.packages("MTS")
if (!"sandwich"%in%inst_pack)
  install.packages("sandwich")
if (!"multDM"%in%inst_pack)
  install.packages("multDM")
if (!"fGarch"%in%inst_pack)
  install.packages("fGarch")
if (!"xtable"%in%inst_pack)
  install.packages("xtable")
if (!"MASS"%in%inst_pack)
  install.packages("MASS")
if (!"glmnet"%in%inst_pack)
  install.packages("glmnet")
if (!"pROC"%in%inst_pack)
  install.packages("pROC")

# Load the required R-libraries
# Standard filter package
library(mFilter)
# Multivariate time series: VARMA model for macro indicators: used here for simulation purposes only
library(MTS)
# HAC estimate of standard deviations in the presence of autocorrelation and heteroscedasticity
library(sandwich)
# Library for Diebold-Mariano test of equal forecast performance
library(multDM)
# GARCH model: for improving regression estimates
library(fGarch)
# Library for tables
library(xtable)
# Packages for Ridge and LASSO
library(MASS)
library(glmnet) 
# Extended time series
library(xts)
# Extended time series
library(pROC)
